\documentclass[9pt]{developercv} 
\usepackage{multicol}
\setlength{\columnsep}{0mm}

\begin{document}

%	TITLE AND CONTACT INFORMATION
\begin{minipage}[t]{0.45\textwidth} 
	\vspace{-\baselineskip} 
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Al Amru Bil Maruf}}}}
	
	\vspace{6pt}
	
	{\Large Software Engineer} 
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} 
	\vspace{-\baselineskip} 
	
    \icon{Phone}{11}{+8801788268495} \\
    \icon{MapMarker}{11}{Dhaka, Bangladesh} \\
	
\end{minipage}
\begin{minipage}[t]{0.3\textwidth} 
	\vspace{-\baselineskip}
	
	\icon{Envelope}{11}{\href{mailto:alamrubilmaruf412@gmail.com}{alamrubilmaruf412@gmail.com}} \\	
    \icon{Github}{11}{\href{https://mortytheplatypus.github.io/}{mortytheplatypus.github.io}} \\  
    
\end{minipage}

%	SKILLS
\cvsect{Skills}
\vspace{-6pt}

\begin{minipage}[t]{0.2\textwidth}
    \textbf{Languages:}
\end{minipage}
\hfill
\begin{minipage}[t]{0.8\textwidth}
  {\large \texttt{Java, JavaScript, Go, Python, C/C++, Bash}}
\end{minipage}

\begin{minipage}[t]{0.2\textwidth}
    \textbf{Frameworks:}
\end{minipage}
\hfill
\begin{minipage}[t]{0.8\textwidth}
  {\large \texttt{Spring Boot, React, Next.js, Express.js, Flask}}
\end{minipage}

\begin{minipage}[t]{0.2\textwidth}
    \textbf{Databases:}
\end{minipage}
\hfill
\begin{minipage}[t]{0.8\textwidth}
  {\large \texttt{MySQL, PostgreSQL, MongoDB, Cassandra}}
\end{minipage}

\begin{minipage}[t]{0.2\textwidth}
    \textbf{Infrastructure:}
\end{minipage}
\hfill
\begin{minipage}[t]{0.8\textwidth}
  {\large \texttt{Nginx, Docker, Kafka, Redis, CDN, RTMP, HLS, Coroot}}
\end{minipage}

\begin{minipage}[t]{0.2\textwidth}
    \textbf{Tools/Protocols:}
\end{minipage}
\hfill
\begin{minipage}[t]{0.8\textwidth}
  {\large \texttt{Git, Liquibase, Locust, Websocket, JWT}}
\end{minipage}

%	EXPERIENCE
\cvsect{Experience}
\begin{entrylist}
    \entry
        {June 2024 \\ onwards}
        {Synesis IT PLC}
        {Software Engineer}
        {Core contributor to \href{https://convay.com}{Convay}, a high-scale video conferencing platform.
        \begin{itemize}\setlength\itemsep{0.05em}
            \item \textbf{Infrastructure Optimization:} Architected an HLS edge-caching strategy that resolved critical bottlenecks where 32-core CPUs were maxing out at 1Gbps; successfully scaled delivery to 10k+ concurrent viewers with near-zero increase in origin load.
            % \item \textbf{System Resilience:} Engineered an RTMP ingest proxy with automatic origin failover and implemented token-based security for HLS playlists to prevent unauthorized access.
            \item \textbf{Load Testing:} Designed and executed simulations for 12k live WebSocket participants using Locust, identifying and fixing distributed messaging bottlenecks in the Spring Boot/Kafka layer.
            \item \textbf{Feature Development:} Developed RBAC, scheduling logic, and custom end-to-end messaging protocols for the core meeting engine.
            \item \textbf{Observability:} Utilized Coroot to monitor system health and proactively debug performance regressions in production.
        \end{itemize}
        \textbf{Tech Stack:} {\large \texttt{Spring Boot, React, Kafka, Docker, Nginx, Cassandra, MySQL, Liquibase}}
        }
\end{entrylist}
\begin{entrylist}
    \entry
        {December 2023 -- \\ May 2024}
        {Sentien IO}
        {Frontend Engineer}
        {Lead the frontend development and UI/UX design for this AI-driven interview preparation platform.
        \begin{itemize}\setlength\itemsep{0.05em}
            \item \textbf{Core User Journey:} Developed a multi-step flow for interviewer selection, resume uploading, and targeted role tracking.
            \item \textbf{Dashboards \& Analytics:} Developed interactive user portals to manage saved jobs, track interview histories, and visualize actionable post-interview feedback via dynamic charts and gamified metrics.
        \end{itemize}
        \textbf{Tech Stack:} {\large \texttt{React, Next.js, TypeScript, Tailwind CSS, Recharts}} 
        }
\end{entrylist}
\begin{entrylist}
	\entry
        {May 2023 -- \\ June 2023}
		{MYSOFT LIMITED}
		{Health Analytics Intern}
		{Developed a real-time health analytics dashboard to visualize hospital data trends.
        \begin{itemize}\setlength\itemsep{0.05em}
            \item Processed multi-dimensional health datasets to identify regional and seasonal disease outbreaks based on patient demographics (age, gender, location).
            \item Built a full-stack application using Flask and Angular to provide hospital administrators with actionable insights into operational overhead.
        \end{itemize}
		\textbf{Tech Stack}: {\large \texttt{Flask, Angular, PostgreSQL}}}
\end{entrylist}

%	PROJECTS
\cvsect{Projects}
\begin{entrylist}
    \entry
		{\texttt{PostgreSQL} \\ \texttt{Spring Boot}}
		{Jwt Authenticator}
		{{\href{https://github.com/mortytheplatypus/jwt-authenticator}{GitHub}}}
		{Developed a reusable full-stack authentication template providing secure registration and session management using JSON Web Tokens (JWT), designed for rapid integration into new web applications.}
    \entry
		{\texttt{Next.js} \\ \texttt{Express.js}}
		{Find My Apartment}
		{{\href{https://github.com/mortytheplatypus/find-my-apartment-api}{Backend}} | {\href{https://github.com/mortytheplatypus/find-my-apartment-frontend}{Frontend}}}
		{Built an apartment-search platform with advanced filtering, personalized recommendation logic, and integrated map views for enhanced user experience.}
    \entry
		{\texttt{Flask} \\ \texttt{React}}
		{Pasteruf}
		{{\href{https://github.com/mortytheplatypus/pasteruf-backend}{GitHub}}}
		{Engineered a dual-purpose platform for persistent text storage and URL shortening. Features automatic redirection logic and a streamlined interface for sharing content across platforms.}
    \entry
		{\texttt{PLSQL} \\ \texttt{React} \\ \texttt{Express.js}}
		{Fantasy Premier League}
		{\href{https://github.com/mortytheplatypus/FantasyPremierLeagueCSE216}{Fantasy Premier League GitHub}}
		{Replicating Fantasy Premier League, which allows users to create fantasy football teams, select players, and compete in leagues.}
    
\end{entrylist}

\newpage

%	EDUCATION
\cvsect{Education}
\begin{entrylist}
    \entry
		{2019 --- 2024}
		{Bangladesh University of Engineering and Technology}
		{BSc in CSE}
		{CGPA: 3.48/4.00 \\
        \textbf{Thesis}: Handwritten Bangla Character Recognition Using Convolutional Neural Networks (CNN)}
\end{entrylist}

%	OTHERS
\cvsect{Others}
    \qquad  - Fluent in Bengali and English \\
    \qquad  - Senior Member and Mentor in Dinajpur Math Club 

\end{document}
